On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-13 paper.tex
Minor
Added some intro

@@

\subsection{Rehmann-Soule theorem}

@@

 \begin{lemma} In the group $G_1$ the following two families of relations are equivalent:
\begin{align} \nonumber \tag{$d_1$}
[[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha + \beta}(a b t),  x_{\gamma}(c t)], & a,b,c \in A,\ \alpha + \beta + \gamma \in \Phi\\
\nonumber \tag{$e_1$}
[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta+\gamma \not\in \Phi. \end{align}
 \end{lemma}

>>>>

The aim of this note is to show that $\K_2$-analogue of Horrocks theorem holds for the unstable group $K_{2, 4}(R)$.
From this we deduce an improved version of Tulenbayev's theorem on early stability for linear $K_2$-groups.

Let $R$ be a commutative ring and $\St(n, R)$ be the Steinberg group of rank $n$.
Denote by $\K_2(n, R)$ (resp. $\K_1(n, R)$) the kernel (resp. cokernel) of the canonical map $\phi\colon \St(n, R) \to \GL(n, R)$.
Recall that in~\cite[Theorem~5.1]{Tu83} M.~Tulenbayev proves the following result.
\begin{thm*} For $n \geq 5$ the Steinberg group functor $\St(n, -)$ satisfies $\mathbb{P}^1$-glueing, i.\,e. for every
 local ring $R$ the following square is pullback:
 \[\xymatrix{ \St(n, R)    \ar[r]\ar[d] & \ar[d] \St(n, R[t^{-1}] \\ 
              \St(\Phi, R[t]) \ar[r]       &        \St(n, R[t, t^{-1}]).}\]
\end{thm*}
The above theorem should be considered as a ``$\K_2$-analogue'' of Horrocks theorem on projective modules (see e.\,g.~\cite[Ch.~IV]{Lam10}).
Recall that this theorem asserts that $\mathbb{P}^1$-glueing holds for the functor $\mathrm{VB}_n$ 
 associating to each commutative ring $R$ the set of rank $n$ vector bundles over $R$.
On the level of $\K_1$ the analogous statement was first obtained by A.~Suslin for the functor $\K_1(n, R)$ under the assumption $n\geq 3$, see~\cite{Su77}.

A lot of effort has been put afterwards into generalizing Suslin's results to other groups (see e.\,g.~\cite{Abe83}). 
One of the more recent results in this direction is~\cite[Theorem~1.1]{St-poly} due to A.~Stavrova, in which
 $\mathbb{P}^1$-glueing for $K_1$ is proved for a large class of isotropic reductive groups.

\subsection{Acknowledgements}
The author would like to thank Anastasia Stavrova and Andrei Lavrenov for numerous helpful discussions regarding this paper.

@@

\subsection{Rehmann-Soul{\'e} theorem}

@@

 \begin{lemma} In the group $G_1$ the following two families of relations are equivalent:
\begin{align} \nonumber \tag{$d_1$}
[[x_{\alpha}(a t), x_{\beta}(b t)],  x_{\gamma}(c)] & = [x_{\alpha + \beta}(a b t),  x_{\gamma}(c t)], & a,b,c \in A,\ \alpha + \beta + \gamma \in \Phi\\
\nonumber \tag{$e_1$}
[[x_{\alpha}(at), x_{\beta}(bt)], x_{\gamma}(ct) ]& = 1, & \alpha + \beta \in \Phi,\ \alpha+\beta \perp \gamma \end{align}
 \end{lemma}
